---
title: "Practice Problem Set 3: Querying and Wrangling Data"
format:
  html:
    code-tools: true
    embed-resources: true
engine: knitr
editor: visual
webr:
  packages: ['dplyr', 'readr', 'ggplot2']
filters:
  - webr
---

1.  Run the following code to load the data:

    ```{r, message = FALSE, warning = FALSE}
    library(tidyverse)
    library(janitor)

    diabetes_dat <- read_csv("../data/diabetes_uci/diabetes_data.csv") %>%
      clean_names()
    ```

2.  Using `tidyverse` syntax, calculate the number of proportion of high BP patients who were diagnosed with diabetes.

    ```{r}

    ```

3.  Calculate the average BMI for smokers:

    ```{r}

    ```

4.  Using the [codebook](https://archive.ics.uci.edu/dataset/891/cdc+diabetes+health+indicators) here, create another variable that contains the corresponding label for the `education` variable. For example, for the rows where `education` is 1, the new variable should contain: `Never attended school or only kindergarten`.

    ```{r}

    ```

5.  For each category of education, calculate the proportion of people who smoke, are physically active, smoke, have had a heart attack, eat fruits and vegetables.

    ```{r}

    ```

6.  Create a `ggplot` representing the data from above.

    ```{r}

    ```

7.  For people with and without diabetes, calculate the mean and standard deviation of the following variables: `mental_hlth`, `physical_htlh`, `gen_hlth`, `bmi`, `age`, `income`.

    ```{r}

    ```

8.  Think of ways to represent the table above in a different way

9.  Restructure the data so that we have mean and standard deviation for diabetic vs non-diabetic people as columns. And, all the background traits for which we calculated the mean and standard deviation as rows.

    ```{r}

    ```

10. Create a table using `gt` or `kable` with the dataset above.

    ```{r}

    ```
