---
title: "Functions and Iteration"
author: "Megha Joshi"
execute: 
  echo: TRUE
format: 
  revealjs:
    theme: [../slides.scss]
    slide-number: c/t
    show-slide-number: all
    title-slide-attributes:
      data-background-color: "#562457"
    preview-links: true
    footer: |
      Theme by Beatriz Mills on  [GitHub](https://github.com/beatrizmilz/quarto-rladies-theme)
editor: visual
---

# Functions {.inverse}

## Example Dataset

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(janitor)
library(evalITR)
library(estimatr)
library(broom)

star_dat <- star %>%
    clean_names()

glimpse(star_dat)
```

## Run a Linear Regression to Assess the Impact of Treatment on Language

```{r}
lang_mod <- lm_robust(g3tlangss ~ treatment + gender + race + schlurbn + grdrange + gkenrmnt, 
                  data = star_dat,
                  se_type = "HC2")

summary(lang_mod)
```

## Tidy Language

```{r}
tidy(lang_mod) %>%
    filter(term == "treatment") %>%
    mutate(outcome = "g3tlangss") %>%
    dplyr::select(outcome, everything())
```

## On Math

```{r}
math_mod <- lm_robust(g3tmathss ~ treatment + gender + race + schlurbn + grdrange + gkenrmnt, 
                  data = star_dat,
                  se_type = "HC2")

summary(math_mod)
```

## Tidy Math

```{r}
tidy(lang_mod) %>%
    filter(term == "treatment") %>%
    mutate(outcome = "g3tlangss") %>%
    dplyr::select(outcome, everything())


```

## On Reading

```{r}
read_mod <- lm_robust(g3tlangss ~ treatment + gender + race + schlurbn + grdrange + gkenrmnt, 
                  data = star_dat,
                  se_type = "HC2")

summary(read_mod)
```

## Tidy Reading

```{r}
tidy(read_mod) %>%
    filter(term == "treatment") %>%
    mutate(outcome = "g3tlangss") %>%
    dplyr::select(outcome, everything())
```

## Repetition

-   Redundant code

-   Repetitive

-   Prone to error when copy and pasting and changing a few things. Can list out all the errors I made?

-   If we want to change the model, let's say add few other variables, we have to repeat that correction multiple times

    -   Which may also open up space for more error

## Functions

## Function Example

```{r}
run_reg <- function(dat = star_dat,
                    outcome_var) {

    lm_equation <- paste(outcome_var, " ~  treatment + gender + race + schlurbn + grdrange + gkenrmnt")

    mod <- lm_robust(as.formula(lm_equation), 
                     data = dat,
                     se_type = "HC2")

    res_clean <- tidy(mod) %>%
        filter(term == "treatment") %>%
        mutate(outcome = outcome_var) %>%
        dplyr::select(outcome, everything())

                
    return(res_clean)
    
}
```

## Run the Function

```{r}
run_reg(outcome = "g3tlangss")
run_reg(outcome = "g3tmathss")
run_reg(outcome = "g3treadss")
```

## Repetition

-   For the sake of this presentation, I am only showing three outcomes.

-   Imagine if there were more than 10 outcomes that you needed to analyze.

-   Think of potential issues in this situation - both when doing brute force analysis and even when using a function like `run_reg().`

# Iteration {.inverse}

## Repetitive Tasks Examples

-   Running analysis for multiple outcomes like above

-   Read in 50 csv files in a folder with data on different years

-   Conduct power analysis to estimate sample size for a randomized trial based on multiple assumed values effect size

## For Loops

-   Classic way to run repetitive analyses or tasks

-   For each item in a vector of items, run the code

## For Loops Example

```{r}
numbers <- 1:10 # A vector of items to loop through

for(n in numbers){ # for each number in the vector numbers
  
  x <- n * 2 # multiply the number by 2
  
  print(x) # print the result
  
  
}
```

## STAR Analysis Example: Loop through Outcomes

```{r}
outcome <- c("g3tlangss", "g3tmathss", "g3treadss") # outcomes to loop through

res <- NULL # initialize the results 

for(y in outcome){ # for each outcome in the outcome vector 
  
  output <- run_reg(outcome = y) # run run_reg for that outcome
  res <- bind_rows(res, output) # append the output to res
  
  
}

res # look at res after the looping

```

## For Loops are Slow...

::: columns
::: {.column width="50%"}
-   For loops are still clunky and involve fairly extensive coding

```{=html}
<!-- -->
```
-   Need to think through how to append and store the outcome or print the outcome

-   Also a bit slow..(er than other stuff we are going to talk about) in R
:::

::: {.column width="50%"}
<iframe src="https://giphy.com/embed/ytPdmmKAsFOUM" width="343" height="480" style frameBorder="0" class="giphy-embed" allowFullScreen>

</iframe>

`<p><a href="https://giphy.com/gifs/tortoise-ytPdmmKAsFOUM"`{=html}via GIPHY</a></p>
:::
:::

## Verbs

## `map()`

```{r}
numbers <- 1:10 # vector with items to loop over

# function that you want run
times_two <- function(x){
  x * 2
}

# loop times_two through each number, notice the output
map(numbers, .f = times_two)
```

## Different Output Format

```{r}
map_int(numbers, .f = times_two)
```

## `pmap_dfr`

```{r}
params <- tibble(outcome = c("g3tlangss", "g3tmathss", "g3treadss"))

pmap_dfr(params, .f = run_reg)
```
