---
title: "Querying and Wrangling Data"
author: "Megha Joshi"
execute: 
  echo: TRUE
format: 
  revealjs:
    theme: [../slides.scss]
    slide-number: c/t
    show-slide-number: all
    title-slide-attributes:
      data-background-color: "#562457"
    preview-links: true
    footer: |
      Theme by Beatriz Mills on  [GitHub](https://github.com/beatrizmilz/quarto-rladies-theme)
editor: visual
---

# Functions {.inverse}

## Example Dataset

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(janitor)
library(evalITR)

star_dat <- star %>%
    clean_names()

glimpse(star_dat)
```

## Run a Linear Regression to Assess the Impact of Treatment on Language

```{r}
library(estimatr)
library(broom)

lang_mod <- lm_robust(g3tlangss ~ treatment + gender + race + schlurbn + grdrange + gkenrmnt, 
                  data = star_dat,
                  se_type = "HC2")

summary(lang_mod)

tidy(lang_mod) %>%
    filter(term == "treatment") %>%
    mutate(outcome = "g3tlangss") %>%
    dplyr::select(outcome, everything())
```

## ... on Math

```{r}
math_mod <- lm_robust(g3tmathss ~ treatment + gender + race + schlurbn + grdrange + gkenrmnt, 
                  data = star_dat,
                  se_type = "HC2")

summary(math_mod)

tidy(lang_mod) %>%
    filter(term == "treatment") %>%
    mutate(outcome = "g3tlangss") %>%
    dplyr::select(outcome, everything())
```

## ...on Reading

```{r}
read_mod <- lm_robust(g3tlangss ~ treatment + gender + race + schlurbn + grdrange + gkenrmnt, 
                  data = star_dat,
                  se_type = "HC2")

summary(read_mod)

tidy(read_mod) %>%
    filter(term == "treatment") %>%
    mutate(outcome = "g3tlangss") %>%
    dplyr::select(outcome, everything())
```

## Repetition

-   Redundant code

-   Repetitive

-   Prone to error when copy and pasting and changing a few things

-   If we want to change the model, let's say add few other variables, we have to repeat that correction multiple times

    -   Which may also open up space for more error

## Functions

## Function Example

```{r}
run_reg <- function(dat = star_dat,
                    outcome_var) {

    lm_equation <- paste(outcome_var, " ~  treatment + gender + race + schlurbn + grdrange + gkenrmnt")

    mod <- lm_robust(as.formula(lm_equation), 
                     data = dat,
                     se_type = "HC2")

    res_clean <- tidy(mod) %>%
        filter(term == "treatment") %>%
        mutate(outcome = outcome_var) %>%
        dplyr::select(outcome, everything())

                
    return(res_clean)
    
}
```

## Run the Function 

```{r}
run_reg(outcome = "g3tlangss")
run_reg(outcome = "g3tmathss")
run_reg(outcome = "g3treadss")
```

# Iteration {.inverse}