---
title: "Practice Problem Set 1: Introduction"
format:
  html:
    code-tools: true
    embed-resources: true
engine: knitr
editor: visual
filters:
  - webr
---

### Downloading R and R Studio/Positron

1.  If you don't have R and R Studio/Positron downloaded, please download them:

    -   Download R [here](https://www.r-project.org/).
    -   Download RStudio [here](https://posit.co/downloads/).
    -   Download Positron [here](https://positron.posit.co/download).

2.  If you prefer to use RStudio, please create an [R project](https://r4ds.hadley.nz/workflow-scripts.html#projects) for this class and open that project. Try using the project setup. If using Positron, you don't need to create a project but you can just set up a folder for this course.

3.  Install the following packages:

    ```{r, eval = FALSE}
    install.packages("tidyverse")
    install.packages("readxl")
    install.packages("janitor")
    install.packages("estimatr")
    ```

### Working In R

4.  Open an R script.

5.  Look at the `sleep` data, which is a built in dataset in R.

    ```{r}
    sleep
    ```

6.  Using the `summary()` function from base R, write code to look at the summary of all the variables in the data.

7.  Using the `table()` function, check the how many records are there for each `group`.

8.  Run a linear regression regressing `extra` on `group` and view the summary of the model.

### Working with Quarto

9.  Download Quarto. Create an `html` Quarto document and write a short paragraph on what you expect to gain out of this course in the next 3 months.

10. In the document, check where the working directory is now.

11. Create code snippets on the Quarto document and transfer the code from Question 4 through 8 there.

12. Render the html file.

### Bonus: Version Control

13. If you don't have a GitHub account, [create an account](https://docs.github.com/en/get-started/start-your-journey/creating-an-account-on-github).

14. Create a repository for this class and add the R Project you created for this class to the repository.

15. [Commit and push](https://book.cds101.com/how-to-stage-commit-and-push-to-github-using-rstudio-server.html) changes to remote repository.
