---
title: "Practice Problem Set 4: Relational Data"
format:
  html:
    code-tools: true
    embed-resources: true
engine: knitr
editor: visual
webr:
  packages: ['dplyr', 'readr', 'ggplot2']
filters:
  - webr
---

1.  Run the following code to load the data. Look through [this website](https://nycflights13.tidyverse.org/index.html) to learn more about the data.

    ```{r, warning = FALSE, error=FALSE}
    library(tidyverse)
    library(nycflights13)

    glimpse(airlines)
    glimpse(airports)
    glimpse(flights)
    glimpse(planes)
    glimpse(weather)
    ```

    \

2.  Sketch out the relationship between all the tables in the database. For each dataset, what is the primary key? What are secondary keys?

3.  How many flights operated by Jet Blue departed from EWR in January, 2013?

    ```{r}

    ```

4.  How many flights that departed from JFK in 2013 were manufactured by Boeing? Create a subset of flights data that meet these conditions - departed from JFK in 2013 on planes manufactured by Boeing.

    ```{r}

    ```

5.  For each of the airports in the `flights` data, count the number of flights that departed when there was some precipitation.

    ```{r}

    ```

6.  How many of the flights from Q5 experienced some type of delay? What was the average delay?

    ```{r}

    ```

7.  Break down the delayed flights from Q6 by plane manufacturer and the year manufactured.

    ```{r}

    ```

8.  Are there any flights in the `flights` data for which we do not have matches in the other datasets? Why might there be no matches?

    ```{r}

    ```

9.  How many flights departing from each of the NYC airports were headed to a different time zone? For each airport, calculate the number from flights departing and landing in each of the time zones. E.g. how many departed JFK and landed in America/Chicago time zone, in America/ Los Angeles time zone etc.?

    ```{r}

    ```

10. Extract data on flights departing NYC airports for which we have information on the plane manufacturer.

    ```{r}

    ```
