---
title: "Practice Problem Set 5A: Strings"
format:
  html:
    code-tools: true
    embed-resources: true
engine: knitr
editor: visual
webr:
  packages: ['dplyr', 'readr', 'ggplot2']
filters:
  - webr
---

1.  Run the following code to load the data. View the codebook and other information on the on the data [here](https://github.com/rfordatascience/tidytuesday/blob/main/data/2025/2025-05-06/readme.md).

    ```{r, message = FALSE, warning = FALSE}
    library(tidyverse)

    nsf_data <- tidytuesdayR::tt_load('2025-05-06')
    nsf_terminations <- nsf_data$nsf_terminations

    ```

2.  Separate the project title into the main title and sub-title.

    ```{r}

    ```

3.  Create a subset of the data with projects that have the word STEM in their title.

    ```{r}
    ```

4.  Count the number of grants by `directorate`. Do you see anything odd.

    ```{r}

    ```

5.  Clean up the `directorate` variable and create the table again. Arrange the table in descending order.

    ```{r}

    ```

6.  Count the length of the `org_zip` variable. Look at the distribution of the length.

    ```{r}

    ```

7.  Split the `org_zip` variable into into two variables. First containing the 5 number zip code and the second containing the add-on 4 number code.

    ```{r}

    ```

8.  Challenge problem: Create a graph identifying the most commonly occurring word across the abstracts from grants that are on Ted Cruz's list.

    ```{r}

    ```
