---
title: "Practice Problem Set 5B: Factors"
format:
  html:
    code-tools: true
    embed-resources: true
engine: knitr
editor: visual
webr:
  packages: ['dplyr', 'readr', 'ggplot2']
filters:
  - webr
---

1.  Run the following code to load the data. View the codebook for the data [here](https://meghapsimatrix.quarto.pub/data-analytics-in-r/slides/class_02_data_visualization/class_02_data_visualization.html#/example-dataset-capital-bike-sharing-data).

    ```{r, message = FALSE, warning = FALSE}
    library(tidyverse)

    bike_dat <- read_csv("../data/capital_bike_sharing_uci/capital_bike_sharing.csv")

    glimpse(bike_dat)
    ```

2.  Create a graph like we did in Lecture 2 of the relationship between temperature and total bike rentals. What is odd about this graph?

    ```{r}

    ```

3.  Recode the `season`, `yr`, `mnth`, `holiday`, `weekday`, `workingday`, and `weather-sit` variable.

    ```{r}

    ```

4.  Change the season variable into a factor variable. What are the levels of the variable? Reorder the variable so that we have Summer, Fall, Winter, Spring.

    ```{r}

    ```

5.  Recreate the graph from Q2 with the new reordered variable.

    ```{r}

    ```

6.  Create a bar chart for the `weathersit` variable.

    ```{r}

    ```

7.  Lump together the least frequent two levels and recreate the graph from Q6.

    ```{r}

    ```
