---
title: "Practice Problem Set 2: Data Visualization"
format:
  html:
    code-tools: true
    embed-resources: true
engine: knitr
editor: visual
r:
  packages: ['dplyr', 'readr', 'ggplot2', 'MatchIt']
filters:
  - r
---

1.  Run the following code to load the data. Glimpse the data and learn about the variables:

    ```{r}
    #install.packages("MatchIt")
    library(MatchIt)
    lalonde
    ```

    **For the following questions, please create a graph using ggplot to answer:**

2.  Create a plot examine the distribution of `ret78` variable which has information on income of the participants in year 1978

    ```{r}

    ```

3.  Now check the difference between the distribution of that variable between the treatment and control groups.

    ```{r}

    ```

4.  Think about one more different way to visualize the difference in the distribution of `ret78` in treatment versus control. Which way do you prefer - one from Q3 or Q4 - and why?

    ```{r}

    ```

5.  Create graphs showing the difference in treatment and control group distributions of the other variables in the data :

    ```{r}

    ```

6.  Examine the relationship between `age` and `educ`

    ```{r}

    ```

7.  Does the relationship between age and education differ between the treatment and control groups:

    ```{r}

    ```

8.  Examine the relationship between race and income in 1978.

    ```{r}

    ```

9.  Does the relationship differ by treatment level.

    ```{r}

    ```

10. **Challenge Problem**: Examine the trend in income across the three times given (1974, 1975, 1978). Draw conclusions about the trends.

    ```{r}

    ```
